Delta Factor - A New Authorization Factor

### 2022-08-07 paper1.tex
updates

\noindent
How the Delta factor works:\\
Since most authentication methods can be mitigated by applying modern phishing toolkits,
they can be detected through \textit{network traffic}.
There are numerous methods to validate the user through various methods, but \textit{few \textbf{server} authentication methods}.
We propose reverse 2FA authentication method to \textbf{validate the server from the client perspective}.
We to want validate the link between the server plus client, by fingerprinting common \textbf{connection} details and independently verifying shared secrets.\\

% Paragraph 6: introduction of RF techniques 		[Actually Delta factor/COTP]
\noindent
A synopsis on \textbf{COTP} is created by:\\
\noindent
A high e, (entropy) shared secret,\\
extraction of shared low level network features,\\
creating a shared time frame,\\ 
creating a composite secret from from the features and high-e secret,\\
generating a hash from the composite secret,\\
% Compress/Truncate hash, Yielding a Connection_based OTP
having the \textit{server} send the generated COTP, and\\
comparing the client and server COTPs. At this point, the connection is accepted or declined.\\

\noindent
The Implementation Details are design goals, high-level limitations, implementation details on the server side as well as the client side, and system integration\\

% frame 16 - Interesting Implementation Limitations

@@

>>>>

\noindent
The Implementation Details are design goals, high-level limitations, implementation details on the server side as well as the client side, and system integration\
\noindent
Standard modules are built into NGINX to extract TLS and TCP connection data. They then pass the details onto a Python WebApp for further validation. In addition, SQLite3 is the user DB,\\

@@

%--------------------------------------------------------------------------------------------------------------------
\section{Algorithm: \textit{implementation details}}
\noindent
Algorithm fundamentals:\\
Since most authentication methods can be mitigated by applying modern phishing toolkits,
they can be detected through \textit{network traffic}.
There are numerous methods to validate the user through various methods, but \textit{few \textbf{server} authentication methods}.
We propose reverse 2FA authentication method to \textbf{validate the server from the client perspective}.
We to want validate the link between the server plus client, by fingerprinting common \textbf{connection} details and independently verifying shared secrets.\\

% Paragraph 6: introduction of RF techniques 		[Actually Delta factor/COTP]
\noindent
Algorithm design:\\
A synopsis on \textbf{COTP} is created by:\\
\noindent
A high e, (entropy) shared secret,\\
extraction of shared low level network features,\\
creating a shared time frame,\\ 
creating a composite secret from from the features and high-e secret,\\
generating a hash from the composite secret,\\
% Compress/Truncate hash, Yielding a Connection_based OTP
having the \textit{server} send the generated COTP, and\\
comparing the client and server COTPs. At this point, the connection is accepted or declined.\\
